Fasano Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2020-12-17 journalMS/article.tex
journal article revisions and updated bib

The Kolmogorov--Smirnov (KS) is a non--parametric method for determining whether a sample is consistent with a given probability distribution. First derived by Kolmogorov and Smirnov \citep{KStest}, the was developed in 1-D. There is still a desire to be able to test 2-D and higher distributions against eachother. As a result, the first 2-D KS test was articulated by Peacock \citep{Peacock1983}.

@@

The Kolmogorov--Smirnov (KS) test is a non--parametric method for determining where a sample is consistent with a given probability distribution. While a complete discussion of the 1-D KS test can be found elsewhere, we will present a brief overview as motivation for the basis and intuition of the 2-D KS test.

>>>>

The Kolmogorov--Smirnov (KS) is a non--parametric method for determining whether a sample is consistent with a given probability distribution. First derived by Kolmogorov and Smirnov \citep{Kolmogorov1933,Smirnov1948}, the was developed in 1-D. There is still a desire to be able to test 2-D and higher distributions against eachother. As a result, the first 2-D KS test was articulated by Peacock \citep{Peacock1983}.

@@

The Kolmogorov--Smirnov (KS) test is a non--parametric method for determining where a sample is consistent with a given probability distribution. While a comprehensive discussion and intracies of the 1-D KS test can be found elsewhere\citep{Stephens1992}, we will present a brief overview as motivation for the basis and intuition of the 2-D KS test.
